\thetitle

### 2021-05-19 writing/introduction.tex
fix small words, vspace for table on pg. 4

The paper's {\it second contribution\/} is a set of {\em results from
applying the evaluation method to three distinct checking regimes for
gradual types and their blame assignment
strategies in approximately 72,000 different scenarios\/} (see
sec.~\ref{sec:results}): (1)~{\it Transient\/}, i.e. Reticulated's
inlined type assertions and collaborative tracking of typed/untyped boundaries~\citep{vss-popl-2017}; (2)~{\it
Natural\/}, i.e. Typed Racket's use of a higher-order contract system and
its blame assignment~\citep{ff-icfp-2002}; and (3) {\it Erasure\/}, i.e.
the approach of industrial systems, which forgo type checks and blame in favor of error
messages from the safety checks of the underlying language. The results
(see sec.~\ref{sec:discussion}) are at least somewhat surprising.  In
principle they validate the conjectures behind the work of theoreticians.
Type checks and blame work together to help with the search for
impedance mismatches between the specified types and the behavior of
untyped components.  Natural's wrapper-based type checks and blame tracking are
more useful than Transient's type in-lined assertions and ``collective blame'' tracking algorithm,
which in turn are superior to Erasure. {\em But\/}, the application of the
method also indicates problems with the expectations of theoreticians. 
In contrast with the theoretical differences between the methods,
{\it Natural\/} is only marginally more useful than {\it Transient\/}, and neither of the two
checking and blame assignment methods are highly superior to {\it Erasure\/}. Additionally, 
the cost of Transient's blame can be huge.  In turn, these
problems suggest that, on one hand, the existing theory does not properly
predict the behavior of blame in real systems with real programs,
and on the other hand, the existing practice lacks data and alternative
experiments to assess the entire landscape of the pragmatics of blame.

>>>>

The paper's {\it second contribution\/} is a set of {\em results from
applying the evaluation method to three distinct checking regimes for
gradual types and their blame assignment
strategies in approximately 72,000 different scenarios\/} (see
sec.~\ref{sec:results}): (1)~{\it Transient\/}, i.e. Reticulated's
inlined type assertions and collaborative tracking of typed/untyped boundaries~\citep{vss-popl-2017}; (2)~{\it
Natural\/}, i.e. Typed Racket's use of a higher-order contract system and
its blame assignment~\citep{ff-icfp-2002}; and (3) {\it Erasure\/}, i.e.
the approach of industrial systems, which forgo type checks and blame in favor of error
messages from the safety checks of the underlying language. The results
(see sec.~\ref{sec:discussion}) are at least somewhat surprising.  In
principle they validate the conjectures behind the work of theoreticians.
Run-time type checks and blame work together to help with the search for
impedance mismatches between the specified types and the behavior of
untyped components.  Natural's wrapper-based type checks and blame tracking are
more useful than Transient's type in-lined assertions and ``collective blame'' tracking algorithm,
which in turn are superior to Erasure. {\em But\/}, the application of the
method also indicates problems with the expectations of theoreticians. 
In contrast with the theoretical differences between the methods,
{\it Natural\/} is only marginally more useful than {\it Transient\/}, and neither of the two
checking and blame assignment methods are highly superior to {\it Erasure\/}. Additionally, 
the cost of Transient's blame can be huge.  In turn, these
problems suggest that, on one hand, the existing theory does not properly
predict the behavior of blame in real systems with real programs,
and on the other hand, the existing practice lacks data and alternative
experiments to assess the entire landscape of the pragmatics of blame.
